Key Derivation From Noisy Sources With More Errors Than Entropy

### 2014-09-17 constantRate/ConstCompFuzzExt-reorg.tex
modifying reusability discussion and abstract

\begin{abstract}
Fuzzy extractors convert a noisy source of entropy into a consistent uniformly-distributed key.  In the process of eliminating noise, they  lose some of the entropy of the original source---in the worst case, as much as the logarithm of the number of correctable error patterns. We call what is left after this worst-case loss the \emph{minimum usable entropy}.  Unfortunately, this quantity is negative for some sources that are important in practice. Most known approaches for building fuzzy extractors work in the worst case and cannot be used when the minimum usable entropy is negative.

We construct the first fuzzy extractors that work for a large class of distributions that have negative minimum usable entropy. We present both information-theoretic and computational constructions.In order to avoid the worst-case loss, they necessarily restrict distributions for which they work.

Our first construction is information-theoretic and corrects a constant fraction of Hamming errors over a large alphabet.  In this construction each symbol must contribute fresh entropy.  We then use computational techniques to obtain two constructions with additional properties.

Our second construction requires a constant fraction of symbols to have a constant amount of entropy conditioned on prior symbols. It corrects a sub-constant fraction of errors and supports super-constant size alphabets.  In addition, it is first construction of a reusable fuzzy extractor without assumption on the form of errors that occurs between reuse.  This is impossible in the information-theoretic setting for an arbitrary number of reuses~(Boyen, CCS 2004).

Our third construction corrects a constant fraction of Hamming errors over a large alphabet. It requires high individual entropy of a constant fraction of symbols, but permits symbols to be dependent.

@@

\paragraph{Reusable Fuzzy Extractors}
An additional desirable security property of fuzzy extractors, introduced by Boyen~\cite{Boyen2004}, is called reusability. This property is necessary if a user enrolls the same or correlated values multiple times. For example, if the source is a biometric reading, the user may have to enroll the same biometric with different organizations (after all, most users have only ten fingers and two irises). \bnote{ewww jokes} Each of them will get a slightly different enrollment reading $w_i$, and will run $\gen(w_i)$ to get a key $r_i$ and a helper value $p_i$. Security for each $r_i$ should hold even when an adversary is given all the values $p_1, \dots, p_q$ (and, in case some organizations turn out to compromised or adversarial, a stronger security notion requires security for $r_i$ even in the presence of $r_j$ for $j\neq i$).

@@

%Prime candidate sources for authentication have $\Huse\le 0$.  
Unfortunately, prime candidate sources for authentication have more errors than entropy. 
As an example, the iris is believed to be the best biometric for high security applications~\cite{prabhakar2003biometric}.  Daugman~\cite{daugman2004} designs a transform called IrisCode (using specialized wavelets) to derive a $2048$ bit string from an iris.  Let the outcome of this transform (on different irises) define a distribution $w$.  The precise number of errors that must be tolerated depends on the desired false reject rate.  Even allowing for a false reject rate of up to $80\%$ (i.e., permitting correctness to fail $80\%$ of the time),\bnote{I don't like saying this twice.  Should either say $20\%$ true accept or correctness around $20\%$} a $t$ of approximately $205$ is required. Thus,
\[
\log |B_t|
= \log \sum_{i=0}^{205} {2048 \choose i} \approx 956\,.
\]
In contrast, $w$ is estimated to have about $249$ bits of entropy~\cite{daugman2004}.
There is considerable subsequent research~\cite{gentile2009slic,gentile2009efficient,rathgeb2011combining}, but it does not affect the above comparison dramatically.%\footnote{The work of Hao et al.~\cite[Section 4.3]{hao2006combining} provides a similar analysis but their calculation underestimates the number of possible error patterns; their calculation, which we cannot confirm, is $\Huse \approx 44$.}

@@

Our second construction, which is only computationally secure, is based on digital lockers~\cite{canetti2008obfuscating}. Digital lockers are obfuscated functions that output a secret value only when given the correct input to ``unlock'' the secret. The main idea of the construction is to pick a random $r$ and then lock it up in a digital locker that is unlocked by a random subset of the symbols of $w$. To tolerate errors in the input, this process is repeated several times, so that at least one digital locker can be unlocked using $w'$. Reusability follows from composable obfuscation.

Finally, our third construction tolerates more errors than the second because it uses digital lockers that are unlocked by single symbols of $w$. Of course, hiding an entire $r$ in every locker then becomes too risky, since we do not assume that every symbol has high individual entropy. Instead, we hide a single bit per locker (this simplified version of a digital locker is basically point obfuscation). To tolerate errors, these bits come from an error correcting code. And to make sure that the adversary who learns some bits doesn't learn anything useful about $r$, we don't encode $r$ in the error-correcting code, but rather extract $r$ (using an information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractor~(\lemref{lem:cond and cext})) from the decoded string.

We emphasize that the obfuscation techniques we use are much weaker than general obfuscation, and can be instantiated quite efficiently under appropriate assumptions.
We need a strong version of point obfuscation/digital lockers that remains secure even when several obfuscations of correlated points are composed. While the standard definition of obfuscation \cite{barak2001possibility} does not imply security under composition, we can base our construction on the relaxed notion \lnote{something is weird --- standard definition is not ok for composition , but a relaxed one is ok?} \bnote{In neither definition is composition implied by standalone security.  However it is known how to construct composable VGB obfuscation for the class of functions we need.} of \emph{virtual grey-box} obfuscation introduced in~\cite{bitansky2010strong}. For this notion, \cite{bitansky2010strong} construct composable obfuscation of point programs under particular number-theoretic assumptions. 
Additionally, such obfuscation can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1997towards}.

@@

\medskip
The remainder of this paper is organized as follows: we cover notation and background on obfuscation and error correcting codes in \secref{sec:preliminaries}, describe computational fuzzy extractors in \secref{sec:fuzzy extractors}, and present our two constructions in Sections \ref{sec:construction} and \ref{sec:sampling} respectively.

@@

Information-theoretic fuzzy extractors are obtained by replacing computational distance by statistical distance.  We do make a second definitional modification.  The standard definition of information-theoretic fuzzy extractors considers $\mathcal{W}$  consisting of all distributions of a given entropy.  As described in the introduction, it is impossible to provide security for all distributions with more errors than entropy.  Thus, in both the computational and information-theoretic settings we consider arbitrary families of distributions.

\subsubsection{Reusable Fuzzy Extractors}
\label{sec:reusable}
\bnote{some of this should probably be moved to the introduction}

Ideally, a fuzzy extractor allows a user to authenticate to multiple different services/devices.  That is, instead of creating a single pair $(r, p)$ from an initial reading $w$, we read the noisy source multiple times~($w_1,..., w_q$) and produce $(r_1, p_1),..., (r_q, p_q)$.  This problem is known as a reusable fuzzy extractor~\cite{Boyen2004}.  Boyen considers two versions of the problem, first where the adversary sees $p_1,..., p_q$~(outsider security).  Second where the adversary controls some subset of the servers and sees key generation on arbitrary $p$~(insider security).  
Boyen constructs a outsider reusable cryptographic fuzzy extractor based on the code-offset or the syndrome sketches from~\cite{JW99, DBLP:journals/siamcomp/DodisORS08} instantiated with linear codes. Boyen also transforms this construction in an insider secure construction using random oracles. 
\paragraph{Previous Negative Results}

There are two primary questions about the reusability of a fuzzy extractor.  The first is how often it can be reused, the second is what correlation is allowed between $w_1,..., w_q$.  Boyen~\cite{Boyen2004} considers fuzzy extractors that are reusable an unbounded number of times.  Their construction is secure when the correlations between $w_1,.., w_q$ come from a subgroup of permutations used in the construction of the fuzzy extractor.  They then show information-theoretic fuzzy extractors secure with unbounded reuse can be transformed into their construction~\cite[Theorem 11]{Boyen2004}.  This shows that correlation between $w_1,..., w_q$ must be restricted to this limited class.  There is no reason to expect that noise between repeated readings comes from a well-behaved subgroup of permutations.  Their result can be interpreted as saying that reusability is impractical.

However, this result is inherently information-theoretic, the adversary must exhaust all randomness of the fuzzy extractor and computes statistical distance over exponential size strings.  There are two  restrictions to avoid this result: 1) limit the number of reuses of the fuzzy extractor 2) provide security against computational adversaries.  The second restriction implies the adversary will only observe a polynomial number of invocations of the fuzzy extractor.

We limit the adversary to be computationally bounded~(and thus sees only a limited number of reuses).
%We present a non-adaptive definition and note that our results extend to the adaptive definition presented by Boyen~\cite[Definition 7]{Boyen2004}.\bnote{We need to come back to justifying this or provide a proof that our scheme works in the adaptive setting.}
%\begin{definition}[Insider Reusable Fuzzy Extractors]
%\label{def:reusable fuzz}
%Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.  Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.  Let $W_1,..., W_q$ be a joint distribution such that $\forall i, W_i\in\mathcal{W}$.  Let $(R_i, P_i)$ be the distribution formed by running $\gen$ on the distribution $W_i$.  We say that $(\gen, \rep)$ is $q$-reusable if for all $i$
%\begin{align*}
%\delta^{\mathcal{D}_{s}}(&(R_1, P_1), ..., (R_i, P_i),..., (R_q, P_q), \\
%&(R_1, P_1),..., (U_\kappa, P_i),..., (R_q, P_q)) < \epsilon.
%\end{align*}
%\end{definition}
Our definition is a modified form of the definition of Boyen~\cite[Definition 7]{Boyen2004}.  We discuss definitional differences in \apref{sec:comparing reusability}.

\begin{definition}[Outsider Reusable Fuzzy Extractors]
\label{def:outsider fuzz ext}
Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$ and fix some $W_1 \in \mathcal{W}$.  Let $f_2,.., f_q , D$ be a split adversary.  Define the following game for all $i=1,..., q$:
\begin{enumerate}%[leftmargin=-.6in]
\item[Sampling] The challenger samples $w_1\leftarrow W_1$.
\item[Perturbation] For $i=2,..., q$: the challenger computes $(r_i, p_i)\leftarrow \gen(w_i)$.  Set $w_{i+1} = f_i(w_1, p_1,..., p_i)$.% The output $p_i$ is provided to $\mathcal{A}$, who selects $\delta_i:\mathcal{M}\rightarrow \mathcal{M}$.  The challenger sets $w_{i+1} = \delta_i(w_1)$.
\item[Distinguishing] The advantage of $D$ is
\[
\epsilon_{sec}\overset{def}= \Pr[D(r_1,..., r_{i-1}, r_i, r_{i+1},..., r_q, p_1,..., p_q)=1] - \Pr[D(r_1,..., r_{i-1}, u, r_{i+1},..., r_q, p_1,..., p_q)=1].
\]
where $u$ is a uniformly random string.
\end{enumerate}
Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.  We say that $(\gen, \rep)$ is $(q, s_{sec}, \epsilon_{sec}, f_2,..., f_q)$-reusable if for all $D$ of size at most $s_{sec}$ they win the game with advantage at most $\epsilon_{sec}$.
\end{definition}

@@

\section{Allowing Correlated Symbols}
In the previous two sections, we presented constructions that supported restricted classes of distributions with more errors than entropy.  Unfortunately, both Constructions~\ref{cons:info theoretic} and \ref{cons:sampling} required each symbol to contribute ``fresh'' entropy.  In this section, we present a computational construction that allows for correlation between symbols while still supporting more errors than entropy and correcting a constant fraction of errors.
This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.

@@

\bnote{shorten this discussion?}
The input $w$ is hidden in two different ways.  In locations where $c_j=1$, the block $w_j$ is information-theoretically unknown.
In locations where $c_j=0$, it is hard to find $w_j$ given access to the point obfuscation.
There are two possible reasons for a bit $c_j'$ to be $1$: because the true value was $1$ and because $w_j \neq w_j'$.  However, if a bit $c_j'$ is $0$, this likely means that $w_j=w_j'$ because collisions when $c_j=0$ are unlikely~(occurring with probability $1/|\mathcal{Z}|$).  This is the reason for the use of a code that only corrects $0\rightarrow 1$ flips.

@@

Unfortunately, \consref{cons:first construction} is not a computational fuzzy extractor.  The codewords $c$ are not uniformly distributed and it is possible to learn some bits of $c$~(for the symbols of $W$ without much entropy).  However, we can show that $c$ looks like it has entropy.  We use the notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
\begin{definition}\protect{~\cite[Definition 3]{DBLP:conf/eurocrypt/HsiaoLR07}}
\label{def:hill ent}
Let $(W, S)$ be a pair of random variables.  $W$ has
\emph{HILL entropy} at least $k$ conditioned on $S$,
denoted $H^{\hill}_{\epsilon, s}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s}} ((W, S),(X,S))\leq \epsilon$.
\end{definition} 
We now define a weaker object that outputs computational entropy~(instead of a pseudorandom key).  We call this object a computational fuzzy conductor.  It is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
\begin{definition}
\label{def:comp fuzzy cond}
A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon, s)$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy \defref{def:comp fuzzy extractor}, except the last condition is replaced with the following weaker condition:
\begin{itemize}
\item for any distribution $W\in \mathcal{W}$, the string $r$ has high HILL entropy conditioned on $P$.  That is $H^{\hill}_{\epsilon, s}(R |P)\geq \tilde{m}$.
\end{itemize}
\end{definition}
Computational fuzzy conductors can be converted to computational fuzzy extractors using standard techniques~(see \apref{sec:further defs}).
The following theorem states the construction is a computational fuzzy conductor.  %After proving this theorem we discuss when \consref{cons:first construction} is useful on its own.
\begin{theorem}
\label{thm:main thm first cons}
Let $n$ be a security parameter. Let $\mathcal{Z}$ be an alphabet where $|\mathcal{Z}| \ge 2^{ \omega(\log(n))}$.
Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block distributions over $\mathcal{Z}^\gamma$, for any $q = \poly(n)$.  Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code over $\mathcal{Z}^\gamma$.  Let $\mathcal{O}$ be an $\gamma$-composable VGB obfuscator for point functions with auxiliary inputs. Then for any $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}=H_0(C)-\beta, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \gamma/|\mathcal{Z}|$.
\end{theorem}

@@

\section{Further Definitions}
\subsection{Computational Fuzzy Conductors}
\label{sec:further defs}
A computational extractor is the adaption of a randomness extractor to the computational setting.  Any information-theoretic randomness extractor is also a computational extractor; however, unlike information-theoretic extractors, computational extractors can expand their output arbitrarily via pseudorandom generators once a long-enough output is obtained. We adapt the definition of Krawczyk~\cite{krawczyk2010cryptographic} to the average case:
\begin{definition}
A function $\cext: \zo^\gamma \times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon, s)$-average-case computational extractor} if for all pairs
of random variables $X, Y$ (with $X$ over $\zo^\gamma$) such that
$\tilde{H}_\infty(X|Y) \ge m$, we have $\delta^{\mathcal{D}_{s}}((\cext(X; U_d), U_d, Y), U_\kappa\times
U_d \times Y) \le \epsilon$.
\end{definition}

@@

\subsection{Adapting Reusability to the Computational Setting}
\label{sec:comparing reusability}

@@

\section{Analysis of \consref{cons:first construction}}
\label{sec:construction}
\subsection{Security}
Security of \consref{cons:first construction} is similar to the security of \consref{cons:sampling}.  However, security is more complicated, the main difficulty is that the definition of block unguessable distributions~(\defref{def:block guessable}) allows for certain weak blocks that can easily be guessed.  This means we must limit our indistinguishable distribution to blocks that are difficult to guess.  Security is proved via the following lemma:

>>>>

\begin{abstract}
Fuzzy extractors convert a noisy source of entropy into a consistent uniformly-distributed key.  In the process of eliminating noise, they  lose some of the entropy of the original source---in the worst case, as much as the logarithm of the number of correctable error patterns. For many practical sources, the error tolerance necessary to achieve reliable key derivation is larger than the entropy of the source.  Unfortunately, it is impossible to provide security for all sources with this property.  Most known approaches for building fuzzy extractors work in the worst case and cannot be used when a source has \emph{more errors than entropy}.

In this work, we exploit source structure to construct fuzzy extractors for large classes of sources with more errors than entropy.  Our constructions are for the Hamming metric over symbols of some alphabet $\mathcal{Z}$.  We present both information-theoretic and computational constructions.

Our first construction is information-theoretic and corrects a constant fraction of Hamming errors over a super-constant size alphabet.  In this construction, each symbol must contribute fresh entropy.

Our second construction provides computational security and supports the same type of sources as the first construction.  This construction comes with added feature: reusability.  A reusable fuzzy extractor can be safely reused across multiple noisy readings of the source~(Boyen, CCS 2004).  Previous reusable fuzzy extractors only provide security when the noise between repeated readings comes from a small and unrealistic class. Our construction is secure as long as the fuzzy extractor is secure on each individual reading. Unfortunately, this construction only corrects a sub-constant fraction of errors.  %Computational techniques allow us to show a very sshows that computational assu computationaprovide requires a constant fraction of symbols to have a constant amount of entropy conditioned on prior symbols. It corrects a sub-constant fraction of errors and supports super-constant size alphabets.  In addition, it is first construction of a reusable fuzzy extractor without assumption on the form of errors that occurs between reuse.  This is impossible in the information-theoretic setting for an arbitrary number of reuses~(Boyen, CCS 2004).

Our first two constructions require each symbol of the source to contribute fresh entropy.  Our third construction removes this requirement and allows symbols to be dependent.  Unfortunately, this change requires a significantly larger alphabet.

@@

\paragraph{Reusable Fuzzy Extractors}
An additional desirable security property of fuzzy extractors, introduced by Boyen~\cite{Boyen2004}, is called reusability. This property is necessary if a user enrolls the same or correlated values multiple times. For example, if the source is a biometric reading, the user may enroll the same biometric with different organizations.  Each of them will get a slightly different enrollment reading $w_i$, and will run $\gen(w_i)$ to get a key $r_i$ and a helper value $p_i$. Security for each $r_i$ should hold even when an adversary is given all the values $p_1, \dots, p_q$ (and, in case some organizations turn out to compromised or adversarial, a stronger security notion requires security for $r_i$ even in the presence of $r_j$ for $j\neq i$).  Many traditional fuzzy extractors are not reusable~\cite{Boyen2004,simoens2009privacy,blanton2012non,blanton2013analysis}.

@@

%Prime candidate sources for authentication have $\Huse\le 0$.  
Unfortunately, prime candidate sources for authentication have more errors than entropy. 
As an example, the iris is believed to be the best biometric for high security applications~\cite{prabhakar2003biometric}.  Daugman~\cite{daugman2004} designs a transform called IrisCode (using specialized wavelets) to derive a $2048$ bit string from an iris.  Let the outcome of this transform (on different irises) define a distribution $w$.  The precise number of errors that must be tolerated depends on the desired correctness.  For correctness of around $20\%$, a $t$ of approximately $205$ is required. Thus,
\[
\log |B_t|
= \log \sum_{i=0}^{205} {2048 \choose i} \approx 956\,.
\]
In contrast, $w$ is estimated to have about $249$ bits of entropy~\cite{daugman2004}.
There is considerable subsequent research~\cite{gentile2009slic,gentile2009efficient,rathgeb2011combining}, but it does not affect the above comparison dramatically.%\footnote{The work of Hao et al.~\cite[Section 4.3]{hao2006combining} provides a similar analysis but their calculation underestimates the number of possible error patterns; their calculation, which we cannot confirm, is $\Huse \approx 44$.}

@@

Our second construction, which is only computationally secure, is based on digital lockers~\cite{canetti2008obfuscating}. Digital lockers are obfuscated functions that output a secret value only when given the correct input to ``unlock'' the secret. The main idea of the construction is to pick a random $r$ and lock $r$ in a digital locker that is unlocked by a random subset of the symbols of $w$. To tolerate errors in the input, this process is repeated several times, so that at least one digital locker can be unlocked using $w'$. Reusability follows from composable obfuscation.

Finally, our third construction tolerates more errors than the second because it uses digital lockers that are unlocked by single symbols of $w$. Since we do not assume that every symbol has high individual entropy, hiding an entire $r$ in every locker then becomes too risky, Instead, we hide a single bit per locker (our actual construction uses point obfuscations, which are easier simpler to construct than digital lockers). To tolerate errors, these bits come from an error correcting code. And to make sure that the adversary who learns some bits doesn't learn anything useful about $r$, we don't encode $r$ in the error-correcting code, but rather extract $r$ (using an information-theoretic~\cite{nisan1993randomness} or computational~\cite{krawczyk2010cryptographic} extractor~(\lemref{lem:cond and cext})) from the decoded string.

We emphasize that the obfuscation techniques we use are much weaker than general obfuscation, and can be instantiated quite efficiently under appropriate assumptions.
We need a strong version of point obfuscation/digital lockers that remain secure even when several obfuscations of correlated points are composed. The required notion is 
%While the standard definition of obfuscation \cite{barak2001possibility} does not imply security under composition, we can base our construction on the relaxed notion \lnote{something is weird --- standard definition is not ok for composition , but a relaxed one is ok?} \bnote{In neither definition is composition implied by standalone security.  However it is known how to construct composable VGB obfuscation for the class of functions we need.} 
composable \emph{virtual grey-box} obfuscation introduced in~\cite{bitansky2010strong}. Bitanski and Canetti construct composable obfuscation of point programs under particular number-theoretic assumptions~\cite{bitansky2010strong}. 
Additionally, such obfuscation can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1997towards}.

@@

\medskip
\paragraph{Organization }
The remainder of this paper is organized as follows: we cover notation and fuzzy extractors in \secref{sec:preliminaries}.  Present our information-theoretic construction in \secref{sec:info theory cons} and our two computational constructions in Sections \ref{sec:sampling} and \ref{sec:cor construction}.

@@

Information-theoretic fuzzy extractors are obtained by replacing computational distance by statistical distance.  We do make a second definitional modification.  The standard definition of information-theoretic fuzzy extractors considers $\mathcal{W}$  consisting of all distributions of a given entropy.  As described in the introduction, it is impossible to provide security for all distributions with more errors than entropy.  Thus, in both the computational and information-theoretic settings we consider limited families of distributions.

\subsubsection{Reusable Fuzzy Extractors}
\label{sec:reusable}

Ideally, a fuzzy extractor allows a user to authenticate to multiple different services/devices.  That is, instead of creating a single pair $(r, p)$ from an initial reading $w$, we read the noisy source multiple times~($w_1,..., w_q$) and produce $(r_1, p_1),..., (r_q, p_q)$.  This problem is known as a reusable fuzzy extractor~\cite{Boyen2004}.  There are two primary parameters of the definition: 1) $q$, the reusability of the fuzzy extractor and 2) what class of correlation is allowed between readings $w_i$ and $w_j$.

Boyen considers two versions of the problem, first where the adversary sees $p_1,..., p_q$~(outsider security).  Second where the adversary controls some subset of the servers and sees key generation on arbitrary $p$~(insider security).  
Boyen constructs a outsider reusable cryptographic fuzzy extractor for unbounded $q$ when the correlation between readings is limited to a transitive isometric permutation groups. Boyen transforms this construction to insider security using random oracles. In both constructions, the correlation between  $w_1,..., w_q$ is limited to a transitive isometric permutation group.  Unfortunately, this class of correlation is relatively weak and unrealistic.
%\paragraph{Previous Negative Results}

Boyen~\cite{Boyen2004} considers information-theoretic fuzzy extractors with unbounded reusability.  
However, even for this relatively weak class of correlations, Boyen shows that reusability comes at a real cost~\cite[Theorem 11]{Boyen2004}.  If the correlation between readings contains a set that generates a transitive isometric permutation group, any secure sketch must lose entropy proportional to the number of errors corrected.\footnote{This result strengthens the bounds of~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}, who show this loss is necessary for uniform $W_1$.} This means achieving reusability for sources with more errors than entropy is impossible in this setting.
%\bnote{old stuff}
%Their construction is secure when the correlations between $w_1,.., w_q$ come from a subgroup of permutations used in the construction of the fuzzy extractor.  They then show information-theoretic fuzzy extractors secure with unbounded reuse can be transformed into their construction~\cite[Theorem 11]{Boyen2004}.  This shows that correlation between $w_1,..., w_q$ must be restricted to this limited class.  There is no reason to expect that noise between repeated readings comes from a well-behaved subgroup of permutations.  Their result can be interpreted as saying that reusability is impractical.
%
%However, this result is inherently information-theoretic, the adversary must exhaust all randomness of the fuzzy extractor and computes statistical distance over exponential size strings.  There are two  restrictions to avoid this result: 1) limit the number of reuses of the fuzzy extractor 2) provide security against computational adversaries.  The second restriction implies the adversary will only observe a polynomial number of invocations of the fuzzy extractor.

To overcome this result, we consider computationally bounded adversaries.
%We present a non-adaptive definition and note that our results extend to the adaptive definition presented by Boyen~\cite[Definition 7]{Boyen2004}.\bnote{We need to come back to justifying this or provide a proof that our scheme works in the adaptive setting.}
%\begin{definition}[Insider Reusable Fuzzy Extractors]
%\label{def:reusable fuzz}
%Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.  Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.  Let $W_1,..., W_q$ be a joint distribution such that $\forall i, W_i\in\mathcal{W}$.  Let $(R_i, P_i)$ be the distribution formed by running $\gen$ on the distribution $W_i$.  We say that $(\gen, \rep)$ is $q$-reusable if for all $i$
%\begin{align*}
%\delta^{\mathcal{D}_{s}}(&(R_1, P_1), ..., (R_i, P_i),..., (R_q, P_q), \\
%&(R_1, P_1),..., (U_\kappa, P_i),..., (R_q, P_q)) < \epsilon.
%\end{align*}
%\end{definition}
We modify the definition of Boyen~\cite[Definition 7]{Boyen2004}.  We discuss the differences in \apref{sec:comparing reusability}.

\begin{definition}[Outsider Reusable Fuzzy Extractors]
\label{def:outsider fuzz ext}
Let $\mathcal{W}$ be a family of distributions over $\mathcal{M}$.  Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{W}, \kappa, t)$-computational fuzzy extractor that is $(\epsilon, s)$-hard with error $\delta$.
Fix some $W_1 \in \mathcal{W}$.  Let $f_2,.., f_q , D$ be a split adversary.  Define the following game for all $i=1,..., q$:
\begin{enumerate}%[leftmargin=-.6in]
\item[Sampling] The challenger samples $w_1\leftarrow W_1$.
\item[Perturbation] For $i=2,..., q$: the challenger computes $(r_i, p_i)\leftarrow \gen(w_i)$.  Set $w_{i+1} = f_i(w_1, p_1,..., p_i)$.% The output $p_i$ is provided to $\mathcal{A}$, who selects $\delta_i:\mathcal{M}\rightarrow \mathcal{M}$.  The challenger sets $w_{i+1} = \delta_i(w_1)$.
\item[Distinguishing] The advantage of $D$ is
\begin{align*}
\text{Adv}(D)&\overset{def}= \Pr[D(r_1,..., r_{i-1}, r_i, r_{i+1},..., r_q, p_1,..., p_q)=1]\\ &- \Pr[D(r_1,..., r_{i-1}, u, r_{i+1},..., r_q, p_1,..., p_q)=1].
\end{align*}
where $u$ is a uniformly random string.
\end{enumerate}
$(\gen, \rep)$ is $(q, s_{sec}, \epsilon_{sec}, f_2,..., f_q)$-reusable if for all $D\in\mathcal{D}_{s_{sec}}$ the advantage is at most $\epsilon_{sec}$.
\end{definition}

@@

\section{Allowing Correlated Symbols}
\label{sec:cor construction}
In the previous two sections, we presented constructions that supported restricted classes of distributions with more errors than entropy.  Unfortunately, both Constructions~\ref{cons:info theoretic} and \ref{cons:sampling} required each symbol to contribute ``fresh'' entropy.  In this section, we present a computational construction that allows for correlation between symbols while still supporting more errors than entropy and correcting a constant fraction of errors.
This construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.

@@

%\bnote{shorten this discussion?}
%The input $w$ is hidden in two different ways.  In locations where $c_j=1$, the block $w_j$ is information-theoretically unknown.
%In locations where $c_j=0$, it is hard to find $w_j$ given access to the point obfuscation.
%There are two possible reasons for a bit $c_j'$ to be $1$: because the true value was $1$ and because $w_j \neq w_j'$.  However, if a bit $c_j'$ is $0$, this likely means that $w_j=w_j'$ because collisions when $c_j=0$ are unlikely~(occurring with probability $1/|\mathcal{Z}|$).  This is the reason for the use of a code that only corrects $0\rightarrow 1$ flips.

@@

Unfortunately, \consref{cons:first construction} is not a computational fuzzy extractor.  The codewords $c$ are not uniformly distributed and it is possible to learn some bits of $c$~(for the symbols of $W$ without much entropy).  However, we can show that $c$ looks like it has entropy.  We use the notion of HILL entropy~\cite{DBLP:journals/siamcomp/HastadILL99} extended to the conditional case:
\begin{definition}\protect{~\cite[Definition 3]{DBLP:conf/eurocrypt/HsiaoLR07}}
\label{def:hill ent}
Let $(W, S)$ be a pair of random variables.  $W$ has
\emph{HILL entropy} at least $k$ conditioned on $S$,
denoted $H^{\hill}_{\epsilon, s}(W|S)\geq k$ if there exists a joint distribution $(X, S)$, such that $\Hav(X|S)\geq k$ and $\delta^{\mathcal{D}_{s}} ((W, S),(X,S))\leq \epsilon$.
\end{definition} 
We now define a weaker object that outputs computational entropy~(instead of a pseudorandom key).  We call this object a computational fuzzy conductor.  It is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
\begin{definition}
\label{def:comp fuzzy cond}
A pair of randomized procedures ``generate'' ($\gen$) and ``reproduce'' ($\rep$) is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t$)-computational fuzzy conductor that is $(\epsilon, s)$-hard with error $\delta$ if $\gen$ and $\rep$ satisfy \defref{def:comp fuzzy extractor}, except the last condition is replaced with the following weaker condition:
\begin{itemize}
\item for any distribution $W\in \mathcal{W}$, the string $r$ has high HILL entropy conditioned on $P$.  That is $H^{\hill}_{\epsilon, s}(R |P)\geq \tilde{m}$.
\end{itemize}
\end{definition}
Computational fuzzy conductors can be converted to computational fuzzy extractors using standard techniques~(see \apref{sec:further defs}).
The following theorem states the construction is a computational fuzzy conductor~(proof in \apref{sec:construction analysis}).  
\begin{theorem}
\label{thm:main thm first cons}
Let $n$ be a security parameter. Let $\mathcal{Z}$ be an alphabet where $|\mathcal{Z}| \ge 2^{ \omega(\log(n))}$.
Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block distributions over $\mathcal{Z}^\gamma$, for any $q = \poly(n)$.  Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code over $\mathcal{Z}^\gamma$.  Let $\mathcal{O}$ be an $\gamma$-composable VGB obfuscator for point functions with auxiliary inputs. Then for any $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}=H_0(C)-\beta, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \gamma/|\mathcal{Z}|$.
\end{theorem}

@@

\section{Definitions}
\subsection{Computational Fuzzy Conductors}
\label{sec:further defs}
A computational extractor is the adaption of a randomness extractor to the computational setting.  Any information-theoretic randomness extractor is also a computational extractor; however, unlike information-theoretic extractors, computational extractors can expand their output arbitrarily via pseudorandom generators once a long-enough output is obtained. We adapt the definition of Krawczyk~\cite{krawczyk2010cryptographic} to the average case:
\begin{definition}
A function $\cext: \zo^\gamma \times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon, s)$-average-case computational extractor} if for all pairs
of random variables $X, Y$ (with $X$ over $\zo^\gamma$) such that
$\tilde{H}_\infty(X|Y) \ge m$, we have $\delta^{\mathcal{D}_{s}}((\cext(X; U_d), U_d, Y), U_\kappa\times
U_d \times Y) \le \epsilon$.
\end{definition}

@@

\subsection{Defining Reusability in the Computational Setting}
\label{sec:comparing reusability}

@@

\section{Analysis of \consref{cons:first construction}}
\label{sec:construction analysis}
\subsection{Security}
Security of \consref{cons:first construction} is similar to the security of \consref{cons:sampling}.  However, security is more complicated, the main difficulty is that the definition of block unguessable distributions~(\defref{def:block guessable}) allows for certain weak blocks that can easily be guessed.  This means we must limit our indistinguishable distribution to blocks that are difficult to guess.  Security is proved via the following lemma:
